Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys

### 2024-12-04 paper/climate_change.qmd
fixing model section

>>>>

## Model Takeaways
summary table age and education in predicting likelihood of taking climate actions
the accuracy of the models prediction matches the genuine data
TODO 
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: table-five
#| fig-cap: TODO

# Load the model accuracy data from the saved CSV
model_accuracies <- read.csv(here::here("data/02-analysis_data/model_accuracies.csv"))

# Round numeric columns to whole numbers
model_accuracies[] <- lapply(model_accuracies, function(x) if(is.numeric(x)) round(x) else x)

# Check the first few rows of the data to ensure it loaded and rounded correctly
head(model_accuracies)
